Supplement for Ward et al., 'Reduced diversity and increased specialization of Alaska salmon fishermen' 

### 2017-03-09 salmon/paper/salmon_paper_appendix_v3.Rmd
rearrange appendix

dat.diff = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
dat.diff = dat.diff[which(dat.diff$revenue >= revenueThreshold & dat.diff$revenue.prev >= revenueThreshold), ]
dat.diff = dat.diff[dat.diff$strategy_permit%in%c("S01A","S01E","S01K","S01M",
  "S03A","S03E"),]

@@

@@

seasons$permit[which(seasons$permit=="S 01A")] = "SEAK-seine"
seasons$permit[which(seasons$permit=="S 01E")] = "PWS-seine"
seasons$permit[which(seasons$permit=="S 01K")] = "Kodiak-seine"
seasons$permit[which(seasons$permit=="S 01M")] = "AKP-seine"
seasons$permit[which(seasons$permit=="S 03A")] = "SEAK-gillnet"
seasons$permit[which(seasons$permit=="S 03E")] = "PWS-gillnet"

appendixPlot0_p1 = ggplot(seasons, aes(year, q, color = permit, group=permit)) + geom_line() + xlab("Year") + ylab("Mean julian day")
appendixPlot0_p2 = ggplot(seasons, aes(year, length, color = permit, group=permit)) + geom_line() + xlab("Year") + ylab("Season length")
```

@@

```{r makePlots, echo = FALSE}
appendixPlot1 = ggplot(agg.annual, aes(year, people, colour = specDiv)) + geom_line() + facet_wrap(~ strategy_permit, scale="free") + ylab("Participation") + xlab("Year")

appendixPlot2_p1 = ggplot(agg.diff, aes(specDiv, log(meanrev), colour = cv, label=strategy_permit)) + xlab("Species diversity") +ylab("Ln (mean revenue)") + geom_text(size=2)
appendixPlot2_p2 = ggplot(agg.diff, aes(specDiv, cv, colour = log(meanrev), label=strategy_permit)) + xlab("Species diversity") +ylab("CV") + geom_text(size=2)
appendixPlot2_p3 = ggplot(agg.diff, aes(log(meanrev), cv, colour = specDiv, label=strategy_permit)) + ylab("CV") + xlab("Ln (mean revenue)") + geom_text(size=2)
```

@@

```{r figa1, fig.cap="Participation (unique people). Permits are coded by gear ('01'=seine, '03' = drift gillnet, '04' = set gillnet) and region ('A'=SEAK, 'D'=Yakutat, 'E'=PWS, 'H'=Cook Inlet, 'K'=Kodiak', 'L'=Chignik, 'M' = Alaskan Peninsula', 'T'=Bristol Bay', 'W'=Kotzebue). Effective species diversity is calculated as 1/Simpson's Diversity.", fig.pos="placeHere", echo=FALSE}
print(appendixPlot1)
```

@@

```{r figa2, fig.cap="Diversity, mean revenue and CV (aggregated across years). Permits are coded by gear ('01'=seine, '03' = drift gillnet, '04' = set gillnet) and region ('A'=SEAK, 'D'=Yakutat, 'E'=PWS, 'H'=Cook Inlet, 'K'=Kodiak', 'L'=Chignik, 'M' = Alaskan Peninsula', 'T'=Bristol Bay', 'W'=Kotzebue). Effective species diversity is calculated as 1/Simpson's Diversity.", fig.pos="placeHere", echo=FALSE}
gridExtra::grid.arrange(appendixPlot2_p1,appendixPlot2_p2,appendixPlot2_p3, ncol=2)
```

@@

g1 = group_by(cfec.raw[cfec.raw$p_fshy=="S 01A" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("SEAK-seine") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]), name="Species",
    labels =c("Chinook","Chum","Coho","Pink","Sockeye")) + theme(legend.position="none")

@@

g3 = group_by(cfec.raw[cfec.raw$p_fshy=="S 01K" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("Kodiak-seine") + theme(legend.position="none") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]))

g4 = group_by(cfec.raw[cfec.raw$p_fshy=="S 01M" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("AKP-seine") + theme(legend.position="none") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]), name = "Species", labels =c("Chinook","Chum","Coho","Pink","Sockeye")) + theme(legend.position="none")

g5 = group_by(cfec.raw[cfec.raw$p_fshy=="S 03A" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("SEAK-gillnet") + theme(legend.position="none") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]))

@@

```{r figa3, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying species composition and effective species diversity (1 / Simpson's Diversity), by permit for seine fisheries in Southeast Alaska (S01A), Prince William Sound (S01E) and Kodiak (S01K). Species are colored as follows: green (Chinook), purple (chum), silver  (coho), pink (pink), red (sockeye)", fig.height=3.2}
gridExtra::grid.arrange(g1, g2, g3, h1, h2, h3, nrow=2)
```

```{r figa4, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying species composition and effective species diversity (1 / Simpson's Diversity), by permit, for seine fisheries on the Alaska Peninsula (S01M), and gillnet fisheries in Southeast Alaska (S03A) and Prince William Sound (S03E).", fig.height=3.2} 
gridExtra::grid.arrange(g4, g5, g6, h4, h5, h6, nrow=2)
```

@@

df$permits[which(df$permits=="S01A")] = "SEAK-seine"
df$permits[which(df$permits=="S01E")] = "PWS-seine"
df$permits[which(df$permits=="S01K")] = "Kodiak-seine"
df$permits[which(df$permits=="S01M")] = "AKP-seine"
df$permits[which(df$permits=="S03A")] = "SEAK-gillnet"
df$permits[which(df$permits=="S03E")] = "PWS-gillnet"

@@

ggplot(df[df$diversity==1,], aes(x=years,y=pred,group=permits)) +
  geom_line() +
  geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  facet_wrap(~permits) + xlab("Year") + ylab("Predicted marginal benefit (ln $)") + geom_hline(yintercept=0, color="red")

@@

yearpermit2 = yearpermit
yearpermit2$permit[which(yearpermit2$permit=="S01A")] = "SEAK-seine"
yearpermit2$permit[which(yearpermit2$permit=="S01E")] = "PWS-seine"
yearpermit2$permit[which(yearpermit2$permit=="S01K")] = "Kodiak-seine"
yearpermit2$permit[which(yearpermit2$permit=="S01M")] = "AKP-seine"
yearpermit2$permit[which(yearpermit2$permit=="S03A")] = "SEAK-gillnet"
yearpermit2$permit[which(yearpermit2$permit=="S03E")] = "PWS-gillnet"

ggplot(data=yearpermit2) + 
  geom_ribbon(aes(x=year,ymin=b0_low,ymax=b0_hi),alpha=0.3) +
  geom_line(aes(x=year,y=b0)) + 
  facet_wrap(~permit) + xlab("Year") + 
  ylab("Intercepts on mean") + 
  geom_hline(yintercept=0, color="red")
```

@@

ggplot(data=rbind(df.gen,df.spec), aes(year, mean, group=strategy, fill=strategy)) + geom_ribbon(aes(ymin=low,ymax=hi), alpha=0.5) + geom_hline(yintercept=0, color="red")

@@

ggplot(data=pinkPWS, aes(b0, diff,color=Year)) + geom_point() + stat_smooth(method=lm) + xlab("Estimated intercept from model") + ylab("Change in total pink salmon returns")
```

group_by(cfec.raw[cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, area) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, area) %>%
  ggplot(aes(year, (p)/1e6, group=spec, color = spec)) + geom_line() + facet_wrap(~area, scale="free") +
  ylab("Revenue (millions) ") + xlab("Year")
```

g = group_by(cfec.raw[cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, area) %>%
  summarize(p = mean(g_price))
p1 = group_by(g, spec, area) %>% 
  mutate(p = p/p[which(year==2002)]) %>% 
  group_by(year, area) %>%
  ggplot(aes(year, log(p), group=spec, color = spec)) + geom_line() + facet_wrap(~area) +
  ylab("Ln avg price relative to 2002") + ggtitle("Synchrony in prices: relative change") + xlab("")
p1

p2 = group_by(g, spec, area) %>% 
  ggplot(aes(year, log(p/p_t1), group=spec, color = spec)) + geom_line() + facet_wrap(~area) +
  ylab("Ln price (t/t-1)") + ggtitle("Synchrony in prices: percent change") + xlab("")
p2

g$logdiff = log(g$p/g$p_t1)
p3 = group_by(g, year, area) %>% 
summarize(sd = sd(logdiff,na.rm=TRUE)) %>% ggplot(aes(year, sd, color=area)) + geom_line() + xlab("Year") + ylab("SD of price changes across species") + ggtitle("Synchrony in price fluctuations across species")

>>>>

dat.diff = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
dat.diff = dat.diff[which(dat.diff$revenue >= revenueThreshold & dat.diff$revenue.prev >= revenueThreshold), ]

@@

dat.diff = dat.diff[dat.diff$strategy_permit%in%c("S01A","S01E","S01K","S01M",
  "S03A","S03E"),]

@@

seasons$permit[which(seasons$permit=="S 01A")] = "SE-seine"
seasons$permit[which(seasons$permit=="S 01E")] = "PWS-seine"
seasons$permit[which(seasons$permit=="S 01K")] = "KO-seine"
seasons$permit[which(seasons$permit=="S 01M")] = "AP-seine"
seasons$permit[which(seasons$permit=="S 03A")] = "SE-gillnet"
seasons$permit[which(seasons$permit=="S 03E")] = "PWS-gillnet"

appendixPlot0_p1 = ggplot(seasons, aes(year, q, color = permit, group=permit)) + geom_line() + xlab("Year") + ylab("Mean julian day") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

appendixPlot0_p2 = ggplot(seasons, aes(year, length, color = permit, group=permit)) + geom_line() + xlab("Year") + ylab("Season length") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

@@

```{r makePlots, echo = FALSE}
# rename
agg.annual$label=NA
agg.annual$label[which(agg.annual$strategy_permit == "S01A")] = "SE-seine"
agg.annual$label[which(agg.annual$strategy_permit == "S01E")] = "PWS-seine"
agg.annual$label[which(agg.annual$strategy_permit == "S01H")] = "CI-seine"
agg.annual$label[which(agg.annual$strategy_permit == "S01K")] = "KO-seine"
agg.annual$label[which(agg.annual$strategy_permit == "S01L")] = "CH-seine"
agg.annual$label[which(agg.annual$strategy_permit == "S01M")] = "AP-seine"
agg.annual$label[which(agg.annual$strategy_permit == "S03A")] = "SE-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S03E")] = "PWS-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S03H")] = "CI-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S03M")] = "AP-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S03T")] = "BB-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S03W")] = "KU-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S04D")] = "YA-drift"
agg.annual$label[which(agg.annual$strategy_permit == "S04H")] = "CI-set"
agg.annual$label[which(agg.annual$strategy_permit == "S04K")] = "KO-set"
agg.annual$label[which(agg.annual$strategy_permit == "S04M")] = "AP-set"
agg.annual$label[which(agg.annual$strategy_permit == "S04T")] = "BB-set"

agg.annual = agg.annual[-which(agg.annual$label=="KU-drift"),]
appendixPlot1 = ggplot(agg.annual, aes(year, people, colour = specDiv)) + geom_line() + facet_wrap(~ label, scale="free") + ylab("Participation") + xlab("Year")

aggdiff = agg.diff[which(agg.diff$strategy_permit %in% unique(agg.annual$strategy_permit)),]
aggdiff$label = agg.annual$label[match(aggdiff$strategy_permit, agg.annual$strategy_permit)]

appendixPlot2_p1 = ggplot(aggdiff, aes(specDiv, log(meanrev), colour = cv, label=label)) + xlab("Species diversity") +ylab("Ln (mean revenue)") + geom_text(size=2) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

appendixPlot2_p2 = ggplot(aggdiff, aes(specDiv, cv, colour = log(meanrev), label=label)) + xlab("Species diversity") +ylab("CV") + geom_text(size=2) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

appendixPlot2_p3 = ggplot(aggdiff, aes(log(meanrev), cv, colour = specDiv, label=label)) + ylab("CV") + xlab("Ln (mean revenue)") + geom_text(size=2) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

@@

```{r figa1, fig.cap="Participation (unique people). Permits are coded by gear (purse seine, set and drift gillnets) and region ('AP' = Alaska Peninsula, 'BB' = Bristol Bay, 'CH' = Chignik, 'CI' = Cook Inlet, 'KO' = Kodiak, 'KU' = Kuskokwim, 'PWS' = Prince William Sound, 'SE' = Southeast, 'YA' = Yakutat). Effective species diversity is calculated as 1/Simpson's Diversity.", fig.pos="placeHere", echo=FALSE}
print(appendixPlot1)
```

@@

```{r figa2, fig.cap="Diversity, mean revenue and CV (aggregated across years). Permits are coded by gear (purse seine, set and drift gillnets) and region ('AP' = Alaska Peninsula, 'BB' = Bristol Bay, 'CH' = Chignik, 'CI' = Cook Inlet, 'KO' = Kodiak, 'KU' = Kuskokwim, 'PWS' = Prince William Sound, 'SE' = Southeast, 'YA' = Yakutat). Effective species diversity is calculated as 1/Simpson's Diversity.", fig.pos="placeHere", echo=FALSE}
gridExtra::grid.arrange(appendixPlot2_p1,appendixPlot2_p2,appendixPlot2_p3, ncol=2)
```

@@

g1 = group_by(cfec.raw[cfec.raw$p_fshy=="S 01A" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("SE-seine") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]), name="Species",
    labels =c("Chinook","Chum","Coho","Pink","Sockeye")) + theme(legend.position="none")

@@

g3 = group_by(cfec.raw[cfec.raw$p_fshy=="S 01K" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("KO-seine") + theme(legend.position="none") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]))

g4 = group_by(cfec.raw[cfec.raw$p_fshy=="S 01M" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("AP-seine") + theme(legend.position="none") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]), name = "Species", labels =c("Chinook","Chum","Coho","Pink","Sockeye")) + theme(legend.position="none")

g5 = group_by(cfec.raw[cfec.raw$p_fshy=="S 03A" & cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p), col = as.numeric(as.factor(spec))) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("SE-gillnet") + theme(legend.position="none") + 
scale_colour_manual(values = c('CHNK'=cbPalette[1], 'CHUM'=cbPalette[2], 
    'COHO'=cbPalette[3], 'PINK'=cbPalette[4], 'SOCK'=cbPalette[5]))

@@

```{r figa3, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying species composition and effective species diversity (1 / Simpson's Diversity), by permit for seine fisheries in Southeast Alaska ('SE', S01A), Prince William Sound ('PWS', S01E) and Kodiak ('KO', S01K). Species are colored as follows: green (Chinook), purple (chum), silver  (coho), pink (pink), red (sockeye)", fig.height=3.2}
gridExtra::grid.arrange(g1, g2, g3, h1, h2, h3, nrow=2)
```

```{r figa4, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying species composition and effective species diversity (1 / Simpson's Diversity), by permit, for seine fisheries on the Alaska Peninsula ('AP', S01M), and gillnet fisheries in Southeast Alaska ('SE', S03A) and Prince William Sound ('PWS', S03E).", fig.height=3.2} 
gridExtra::grid.arrange(g4, g5, g6, h4, h5, h6, nrow=2)
```

g1 = group_by(cfec.raw[cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, area) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, area) %>%
  ggplot(aes(year, (p)/1e6, group=spec, color = spec)) + geom_line() + facet_wrap(~area, scale="free") +
  ylab("Revenue (millions) ") + xlab("Year") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g1
```

g = group_by(cfec.raw[cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, area) %>%
  summarize(p = mean(g_price))
p1 = group_by(g, spec, area) %>% 
  mutate(p = p/p[which(year==2002)]) %>% 
  group_by(year, area) %>%
  ggplot(aes(year, log(p), group=spec, color = spec)) + geom_line() + facet_wrap(~area) +
  ylab("Ln avg price relative to 2002") + ggtitle("Synchrony in prices: relative change") + xlab("") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
p1

p2 = group_by(g, spec, area) %>% 
  ggplot(aes(year, log(p/p_t1), group=spec, color = spec)) + geom_line() + facet_wrap(~area) +
  ylab("Ln price (t/t-1)") + ggtitle("Synchrony in prices: percent change") + xlab("") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
p2

g$logdiff = log(g$p/g$p_t1)
p3 = group_by(g, year, area) %>% 
summarize(sd = sd(logdiff,na.rm=TRUE)) %>% ggplot(aes(year, sd, color=area)) + geom_line() + xlab("Year") + ylab("SD of price changes across species") + ggtitle("Synchrony in price fluctuations across species") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

## Causality between lagged abundance and prices

Previous work on long term trends in Alaska salmon markets have highlighted effects of changing production practices, including freezing (Knapp et al. 2012). Caches of frozen salmon from large harvest may have competitive effects on prices 1-2 years later. Using a Granger test for causality between first-differenced time series of harvest and prices, this effect is particularly true for coho and sockeye salmon, where abundance at time *t-1* or *t-2* improves predictions of prices at time *t*.

```{r, echo=FALSE}
library(knitr)
d = read.table("../../salmon/data-generated/granger_table.csv", sep=",", header=TRUE)
kable(d)
```

```{r echo=FALSE, eval=FALSE}
#Z = read.table("../../salmon/data-generated/granger_table_s01a.csv", header=TRUE)
```

@@

df$permits[which(df$permits=="S01A")] = "SE-seine"
df$permits[which(df$permits=="S01E")] = "PWS-seine"
df$permits[which(df$permits=="S01K")] = "KO-seine"
df$permits[which(df$permits=="S01M")] = "AP-seine"
df$permits[which(df$permits=="S03A")] = "SE-gillnet"
df$permits[which(df$permits=="S03E")] = "PWS-gillnet"

@@

g1 = ggplot(df[df$diversity==1,], aes(x=years,y=pred,group=permits)) +
  geom_line() +
  geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  facet_wrap(~permits) + xlab("Year") + ylab("Predicted marginal benefit") + geom_hline(yintercept=0, color="red") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g1
```

@@

yearpermit2 = yearpermit
yearpermit2$permit[which(yearpermit2$permit=="S01A")] = "SE-seine"
yearpermit2$permit[which(yearpermit2$permit=="S01E")] = "PWS-seine"
yearpermit2$permit[which(yearpermit2$permit=="S01K")] = "KO-seine"
yearpermit2$permit[which(yearpermit2$permit=="S01M")] = "AP-seine"
yearpermit2$permit[which(yearpermit2$permit=="S03A")] = "SE-gillnet"
yearpermit2$permit[which(yearpermit2$permit=="S03E")] = "PWS-gillnet"

g1 = ggplot(data=yearpermit2) + 
  geom_ribbon(aes(x=year,ymin=b0_low,ymax=b0_hi),alpha=0.3) +
  geom_line(aes(x=year,y=b0)) + 
  facet_wrap(~permit) + xlab("Year") + 
  ylab("Intercepts on mean") + 
  geom_hline(yintercept=0, color="red") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g1
```

@@

g1 = ggplot(data=rbind(df.gen,df.spec), aes(year, mean, group=strategy, fill=strategy)) + geom_ribbon(aes(ymin=low,ymax=hi), alpha=0.5) + geom_hline(yintercept=0, color="red") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g1
```

```{r, echo=FALSE, fig.pos="placeHere", fig.cap = "Change in natural log of landed weight versus change in effective species diversity, by permit. Decreases in landed weight is often accompanied by reduced catch diversity."}
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
diffdat = filter(diffdat, !is.na(days.change))

g1 = ggplot(diffdat, aes(log(weight)-log(weight.prev), specDiv.change)) + geom_point(alpha=0.15, col="blue", size=0.4) + facet_wrap(~ strategy_permit) + xlab("Change in ln annual landed weight") + ylab("Change in effective species diversity") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g1
```

@@

g1 = ggplot(data=pinkPWS, aes(b0, diff,color=Year)) + geom_point() + stat_smooth(method=lm) + xlab("Estimated intercept from model") + ylab("Change in total pink salmon returns") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g1
```
